A Proposal for Linguistic Similarity Datasets Based on Commonality Lists

### 2016-06-14 paper.tex
Minor changes

Sentential similarity might be treated as the similarity of the heads in the contexts. That is, the similarity between \textit{sees} and \textit{notices} in \textit{John \textbf{sees} Mary} and \textit{John \textbf{notices} a woman}. This approach abstracts away grammatical difference between the sentences and concentrates on semantics and fits the proposed model as the respect for the head, which is a lexical entity, has to be found.

@@

There are several ways in which that sentence can both be \emph{grammaticalised} and \emph{lexicalised}. For example, \textit{No} and \textit{I've seen John eating them} are similar sentences because they lexicalise the same answer to the question \textit{Do we have cookies?} More generally, this gives rise to dialogue act tags: another way of utterance categorisation, refer to the work of \newcite{kalchbrenner-blunsom:2013:CVSC} and \newcite{milajevs-purver:2014:CVSC}.

@@

\paragraph{Language Sub-systems and strategies}

\newcite{Steels2010a} introduces the idea of language sub-systems and language strategies. A language subsystem is a means of expressing certain related or similar meanings. Examples of such sub-systems include:
\begin{compactitem}
    \item Lexical systems which express colours.
    \item Morphological devices to encode tenses.
    \item Usage of word order to express relations between agent and patient.
\end{compactitem}  
The later is an illustration of a language strategy. In English agent-patient relations are mainly encoded by syntax whereas German would use intonation and a combination or articles and case to convey the same information. Russian in contrast will use morphological devices for the same purpose.

@@

In the future, a multi-category similarity dataset should be build that allows evaluation of vector space models of meaning by not only measuring proximity between the points, but also their arrangement to clusters. The same ideas can be used to build phrase and sentence level datasets.

% At the very end, we need to say something about parsimony or "Occam's razor": Among competing hypotheses, the one with the fewest assumptions should be selected.
%We are proposing going into a lot of detail in creating datasets and software. How do we leverage that with wide-coverage?

>>>>

Sentential similarity might be treated as the similarity of the heads in the contexts. That is, the similarity between \textit{sees} and \textit{notices} in \textit{John \textbf{sees} Mary} and \textit{John \textbf{notices} a woman}. This approach abstracts away grammatical difference between the sentences and concentrates on semantics and fits the proposed model as the respect for the head, which is a lexical entity, has to be found \cite{corbett1993heads}.

@@

There are several ways in which a sentence can both be \emph{grammaticalised} and \emph{lexicalised}. For example, \textit{No} and \textit{I've seen John eating them} are similar sentences because they lexicalise the same answer to the question \textit{Do we have cookies?} More generally, this gives rise to dialogue act tags: another way of utterance categorisation, refer to the work of \newcite{kalchbrenner-blunsom:2013:CVSC} and \newcite{milajevs-purver:2014:CVSC}.

@@

\paragraph{Language sub-systems and strategies}

\newcite{Steels2010a} introduces the idea of language sub-systems and language strategies. A language subsystem are the means of expressing certain related or similar meanings. Examples of such sub-systems include:
\begin{compactitem}
    \item Lexical systems which express colours.
    \item Morphological devices to encode tenses.
    \item Usage of word order to express relations between agent and patient.
\end{compactitem}  
The later is an illustration of a language strategy. In English agent-patient relations are mainly encoded by syntax whereas German would use intonation and a combination or articles and case to convey the same information. Russian, in contrast, will use morphological devices for the same purpose.

@@

In the future, a multi-category similarity dataset should be build that allows evaluation of vector space models of meaning by not only measuring proximity between the points, but also their arrangement to clusters. The same ideas can be used to build phrase- and sentence-level datasets.
